**Operating model**

### 2023-02-14 Rmd/report mac.Rmd
report.R and report mac.Rmd

library(captioner)     # captions
tab_nums <- captioner::captioner(prefix = "Table", levels=3, type=c("n","n","n"), infix=".")
fig_nums <- captioner::captioner(prefix = "Figure", levels=3, type=c("n","n","n"), infix=".")

source("../R/dd.R")
source("../R/get_dropbox.r")
source("../R/pm.R")

dropboxdir<-try(file.path(get_dropbox(), "pelagics"))

@@

# ------------------------------------------------------------------------------
# Operating model
# ------------------------------------------------------------------------------
resultsdir <- file.path(dropboxdir, "results", mystk, "figures")

@@

@@

@@

knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_sim_dd_mass.jpg")))

@@

knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_sim_dd_maturity.jpg")))

@@

knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_sim_dd_m.jpg")))

@@

knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_eq_yield.jpg")))

@@

knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_om.jpg")))

>>>>

library(captioner)     # captions
tab_nums <- captioner::captioner(prefix = "Table", levels=2, type=c("n","n"), infix=".")
fig_nums <- captioner::captioner(prefix = "Figure", levels=2, type=c("n","n"), infix=".")

source("../R/dd.R")
source("../R/pm.R")

source("../R/get_dropbox.r")
dropboxdir<-try(file.path(get_dropbox(), "pelagics"))

@@

load(file=file.path(dropboxdir,paste0("data/om/",mystk,"matPar.RData")))

# ------------------------------------------------------------------------------
# Operating model
# ------------------------------------------------------------------------------
figuresdir <- file.path(dropboxdir, "results", mystk, "figures")
tablesdir  <- file.path(dropboxdir, "results", mystk, "tables")

@@

```{r}

tab_nums(name    = "section1_tab", level = 1, display = FALSE)
fig_nums(name    = "section1_fig", level = 1, display = FALSE)

@@

**Weight at age**

[text here]

```{r, echo=FALSE, fig.width=10, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

fig_nums(
  name    = "cond_waa", level = 1, display = FALSE,
  caption = paste0(mystkname, ". Weight at age by year and cohort"))

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "waa.jpg", sep="_")))

_`r fig_nums("cond_waa")`_

**Maturity at age**

[text here]

```{r, echo=FALSE, fig.width=10, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

fig_nums(
  name    = "cond_mat", level = 2, display = FALSE,
  caption = paste0(mystkname, ". Maturity at age by year and cohort"))

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "mat.jpg", sep="_")))

_`r fig_nums("cond_mat")`_

**Natural mortality at age (fixed)**

[text here]

```{r, echo=FALSE, fig.width=10, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

fig_nums(
  name    = "cond_natmor", level = 2, display = FALSE,
  caption = paste0(mystkname, ". Natural mortality at age by year and cohort (all ages and years the same M)"))

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "m.jpg", sep="_")))

_`r fig_nums("cond_natmor")`_

**Density dependence in Weight at age vs. Total biomass**

[text here]

```{r, echo=FALSE, fig.width=10, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

fig_nums(
  name    = "cond_ddwaa", level = 2, display = FALSE,
  caption = paste0(mystkname, ". Density dependence and weight at age."))

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "dd_waa.jpg", sep="_")))

_`r fig_nums("cond_ddwaa")`_

**GAMM at age**

[text here]

```{r, echo=FALSE, fig.width=10, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

fig_nums(
  name    = "cond_gammwaa", level = 2, display = FALSE,
  caption = paste0(mystkname, ". GAMM analysis of density dependence and weight at age."))

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "gamm.jpg", sep="_")))

_`r fig_nums("cond_gammwaa")`_

**GAMM summary**

[text here]

```{r, echo=FALSE, fig.width=10, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

tab_nums(
  name    = "cond_gammsummary", level = 1, display = FALSE,
  caption = paste0(mystkname, ". GAMM summary of density dependence and weight at age."))

cat(readLines(file.path(tablesdir, paste(mystk, "gamm summary.txt", sep="_"))), sep = '\n')

_`r tab_nums("cond_gammsummary")`_

**GAMM summary**

[text here]

```{r, echo=FALSE, fig.width=10, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

tab_nums(
  name    = "cond_gammcoefficients", level = 2, display = FALSE,
  caption = paste0(mystkname, ". GAMM coefficients of density dependence and weight at age."))

cat(readLines(file.path(tablesdir, paste(mystk, "gamm coefficients.txt", sep="_"))), sep = '\n')

_`r tab_nums("cond_gammcoefficients")`_

**LM of density dependence in weight at age**

[text here]

```{r, echo=FALSE, fig.width=10, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

fig_nums(
  name    = "cond_lmwaa", level = 2, display = FALSE,
  caption = paste0(mystkname, ". LM analysis of density dependence and weight at age."))

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "lm_waa.jpg", sep="_")))

_`r fig_nums("cond_lmwaa")`_

**LM summary**

[text here]

```{r, echo=FALSE, fig.width=10, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

tab_nums(
  name    = "cond_lmsummary", level = 2, display = FALSE,
  caption = paste0(mystkname, ". LM summary of density dependence and weight at age."))

cat(readLines(file.path(tablesdir, paste(mystk, "lm summary.txt", sep="_"))), sep = '\n')

_`r tab_nums("cond_gammcoefficients")`_

**DD analysis of maturity at age**

[text here]

```{r, echo=FALSE, fig.width=10, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

fig_nums(
  name    = "cond_ddmat", level = 2, display = FALSE,
  caption = paste0(mystkname, ". Analysis of density dependence and maturity at age."))

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "dd_mat.jpg", sep="_")))

_`r fig_nums("cond_ddmat")`_

**Estimated maturity at weight**

$f(x) = \frac{1}{1+e^{-k(x-x_0)}}$

Estimated parameters: k=`r matPar$par[1]` $W_{50}$=`r matPar$par[2]`

```{r, echo=FALSE, fig.width=10, fig.asp=0.6, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

fig_nums(
  name    = "cond_matogive", level = 2, display = FALSE,
  caption = paste0(mystkname, ". Estimated maturity ogive at weight"))

knitr::include_graphics(path=file.path(figuresdir, paste(mystk, "mat_ogive.jpg", sep="_")))

_`r fig_nums("cond_matogive")` _

@@

# knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_sim_dd_mass.jpg")))

@@

# knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_sim_dd_maturity.jpg")))

@@

# knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_sim_dd_m.jpg")))

@@

# knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_eq_yield.jpg")))

@@

# knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_om.jpg")))
